---
title: "Assessment1-part2"
author: "Yalan Huang S4664845"
date: "20/08/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r}
library(rtweet)
```

```{r}
library(dplyr)
```

#merging and opening all csv files
```{r}
files<-list.files(pattern="\\.csv$",full.names = TRUE) 

```
#remove duplicate entries
```{r}
all_data<-map_df(files,  ~read_csv(.x))
```


```{r}
final_data<-all_data%>%distinct()
```

#look at first 6 obs
```{r}
final_data%>%
  head()

```

#look at structure
```{r}
final_data%>%
  str()
  
```

```{r}
football_short<-final_data%>%
  select(id, in_reply_to_screen_name, created_at, text, favorite_count, retweet_count,place)
```


##Present the first 10 tweets from your dataset using `kable()`

```{r}
library(knitr)

kable(final_data[1:10,],"simple")
```

#Visualise the frequency of your tweets

```{r}
ts_plot(football_short, "hours") +
  labs(x = NULL, y = NULL,
       title = "Frequency of tweets with Football",
       subtitle = paste0(format(min(football_short$created_at), "%d %B %Y"), " to ", format(max(football_short$created_at),"%d %B %Y")),
       caption = "Football tweets Data collected from Twitter") +
  theme_minimal()
```

#Identify top tweeting locations and present the first 10. 
#Write 2-3 sentences on your insights from this.

#This is the top 10 location. Because of the privacy, all the user did not share their location.As a result, there is no data.


```{r}
football_short %>% 
  filter(!is.na(place)) %>% 
  count(place, sort = TRUE) %>% 
  top_n(10)
```


##Identify the most retweeted tweets and present top 20. 

```{r}

football_short %>% 
  arrange(-retweet_count) %>%
  slice(1) %>% 
  select(created_at, in_reply_to_screen_name, text, retweet_count)
```

#top20
```{r}

football_short %>% 
  arrange(-retweet_count) %>%
  select(created_at, in_reply_to_screen_name, text, retweet_count) %>%
  top_n(20)
```

##Identify the most liked tweets and present the first 15. 

```{r}
football_short %>% 
  arrange(-favorite_count) %>%
  top_n(15, favorite_count) %>% 
  select(created_at, in_reply_to_screen_name, text, favorite_count)

```

##Identify top tweeters in your dataset and present the first 5. 

```{r}

football_short %>%
  filter(!is.na(in_reply_to_screen_name)) %>%
  count(in_reply_to_screen_name, sort = TRUE) %>%
  top_n(5) %>%
  mutate(screen_name = paste0("@", in_reply_to_screen_name)) 
```

##Identify top emojis in your dataset and present the first 10.

```{r}
library(emoji)
library(tidyr)
library(tidytext)

```


```{r}
football_short %>% 
  mutate(emoji = emoji_extract_all(text)) %>%
  unnest(cols = c(emoji)) %>%
  count(emoji, sort = TRUE) %>%
  top_n(10)
```

##Identify top hashtags in your dataset and present the first 10. 

```{r}
football_short %>% 
  unnest_tokens(hashtag, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(hashtag, "^#"),
         hashtag != "#foot") %>%
  count(hashtag, sort = TRUE) %>%
  top_n(10)
```

##Identify top mentions in your dataset and present the first 10.


```{r}
football_short %>% 
  unnest_tokens(mentions, text, "tweets", to_lower = FALSE) %>%
  filter(str_detect(mentions, "^@")) %>%  
  count(mentions, sort = TRUE) %>%
  top_n(10)
```

